The challenge and promise of software citation for credit, identification, discovery, and reuse

### 2016-01-17 SC-challenge.tex
If we must ;-)
Update SC-challenge.tex

Modern science and engineering depend on software.
To acknowledge traditional research results published in archival journals and conferences, we use citation, but no such accepted standard exists to credit the considerable efforts that go into software.
One method to increase the amount of software developed, shared and credited is to treat a software release as a publication. 
In addition, since research results, including data, now depend on the specific software used (e.g., version), proper citation---and the associated preservation---is necessary to ensure reproducibility.
\textbf{The main challenge of software citation is that we need a way to uniquely identify released (published) software so that it can be cited by others who use it.}
We also need a process to curate and review software.

@@

However, research and development efforts are needed to solve the remaining challenges.
These questions include: how can we cite closed-source\slash commercial software---can the above information be provided, even if the the software itself is not publicly preserved?
How will index services (e.g., Web of Science, Scopus, Google Scholar) fully index software, since in order for software citations to carry weight akin to publications for academic credit and reputation, they require such indexing to create a similar citation network?
How can publications indicate direct use of software for research in citations, where results would not be possible without efforts of software authors?
Should such a citation be ``weighted'' higher than others?
The \citeN{AAS:2016} suggests a new ``Software'' section below the acknowledgements; other approaches include machine-readable supplementany data~\cite{Katz:2015aa}.

>>>>

Modern science and engineering depend on software.
To acknowledge traditional research results published in archival journals and conferences, we use citation, but no such accepted standard exists to credit the considerable efforts that go into software.
One method to increase the amount of software developed, shared, and credited is to treat a software release as a publication. 
In addition, since research results, including data, now depend on the specific software used (e.g., version), proper citation---and the associated preservation---is necessary to ensure reproducibility.
\textbf{The main challenge of software citation is that we need a way to uniquely identify released (published) software so that it can be cited by others who use it.}
We also need a process to curate and review software.

@@

However, research and development efforts are needed to solve the remaining challenges.
These questions include: how can we cite closed-source\slash commercial software---can the above information be provided, even if the the software itself is not publicly preserved?
How will index services (e.g., Web of Science, Scopus, Google Scholar) fully index software, since in order for software citations to carry weight akin to publications for academic credit and reputation, they require such indexing to create a similar citation network?
How can publications indicate direct use of software for research in citations, where results would not be possible without efforts of software authors?
Should such a citation be ``weighted'' higher than others?
The \citeN{AAS:2016} suggests a new ``Software'' section below the acknowledgements; other approaches include machine-readable supplementary data~\cite{Katz:2015aa}.
